
% Acknowledgments File

\chapter*{\centering{\uppercase{Acknowledgements}}}
\addcontentsline{toc}{chapter}{Acknowledgements}


%\textit{Please insert brief and professional acknowledgements here. They should be no more than one page.} %Please remove this code taking particular care to remove the \textit command which makes use of italic font.

Being grateful for the past PhD adventure, I wish to thank everyone who has helped me along this way. Without their support and encouragement this thesis would be impossible.

First I would like to express my sincere gratitude to my advisor, Prof. Niloy J. Mitra, for his incredible patience and insightful guidance during my study. I have learnt how to conduct analyses on problems, concentrate on research, conclude a project, and, most importantly, not to be afraid to try. Niloy has worked beyond the call of duty on discussing algorithms and even implementations, finalizing papers and examining submissions as well as reviewing presentations. Not only motivated in different research topics, he has also had a great impact on my life, being so kind and respectful. I especially thank Prof.Helmut Pottmann, for his guidance and also for his geometry lectures initializing my understanding of computer graphics.

I would also like to thank my committee members, Prof. Peter Wonka, Prof. Xiangliang Zhang, and Prof. Ying Wu, who provided important advice to my research proposal and the preparation of this thesis. I audited Peter's Computer graphics course and Xiangliang's Data mining course, which inspired me in my research work. I want to thank Prof. Michael Wand, for being my external examiner, and for the impressive collaboration experience with him. His enthusiastic attitude and devotion to the projects have influenced me enormously. I appreciate the enjoyable discussions with Michael on topics from technical solutions to programming questions.

I feel lucky to have spent my time in the visual computing center at KAUST working with many talented people. Many thanks go to everyone, only some of whom are listed, Prof. Wolfgang Heidrich, Prof. Markus Hadwiger, Mrs. Liliana Rivera, Mrs. Tina Smith and Dr. Mohamed Shalaby, for making the lab a pleasant working environment. I met some of my collaborators here, Sawsan AlHalawani, Youyi Zheng and Yongliang Yang, who have also become my friends. Additionally, my friends Chengcheng Tang, Dongming Yan, Yanchao Yang, Xin Zhao, always helped me without hesitation, and made the lab a fun place in those late nights before deadlines. It was valuable to learn from them, how they thought and solved the same problem differently. Thanks to many other friends in the lab, Amal Aboulhassan, Sara Shasheen, Lubin Fan, Xiang Sun, Caigui Jiang, Lee Staff; and out of the lab, Maolida Nihemaiti, Wanyu Huang, Wenwen Zhu; and especially Guoda Chen, for their enduring patience and supports, e.g., on the user studies of my projects helping me improve the design of the user interface.

Finally, my deepest gratitude goes to my whole family, especially to my father, mother and sister. Their endless support and encouragement allowed me to focus on my study and taught me to be thankful even for challenges and setbacks from which I grow and build strength.






% Copyright 2010 Imran Shafique Ansari
% Contact Email: imran.ansari@kaust.edu.sa
% Contact Number: +966 59 897 1005


% Modified by Said Ehrlich 