
% Appendix for Papers

\refstepcounter{chapter}%
\chapter*{\thechapter \quad Papers Published and Submitted}
\label{papers}


$\bullet$ Y. Zheng, ${H. Liu}^\star$, J. Dorsey, and N. J. Mitra, {``SMARTCANVAS: Context-inferred Interpretation of Sketches for Preparatory Design Studies"}, \emph{submitted to Eurographics 2016}. ($\star$: joint first author)\\
$\bullet$ $H. Liu$, U. Vimont, M. Wand, M. P. Cani, S. Hahmann, D. Rohmer, and N. J. Mitra, {``Replaceable Substructures for Efficient Part-Based Modeling"}, \emph{Computer Graphics Forum. Proceedings of Eurographics 2015}, vol. 34, no. 2, 2015, p. 11.\\
$\bullet$ Y. Zheng, $H. Liu$, J. Dorsey, and N. J. Mitra, {``Ergonomics-inspired Geometric Exploration and Reshaping of Model Collections"}, \emph{IEEE Transactions on Visualization and Computer Graphics 2015}\\
$\bullet$ $H. Liu$, Y. L. Yang, S. AlHalawani, and N. J. Mitra, {``Constraint-aware Interior Layout Exploration for Precast Concrete-based Buildings"}, \emph{The Visual Computer / Computer Graphics International 2013}, vol. 29, no. 6-8, pp. 663-673.\\
$\bullet$ S. AlHalawani, Y. L Yang,  $H. Liu$,  and N. J. Mitra, {``Interactive Facades: Analysis and Synthesis of Semi-Regular Facades"}, \emph{Eurographics 2013}, vol. 32, no. 2pt2, 2015, pp. 215-224.\\
$\bullet$ $H. Liu$, X.Zhang, A. Rockwood, {``A Direction Change based Algorithm for Polygonal Approximation"}, \emph{ICPR 2012}



%$\bullet$ Author 1 Name, Author 2 Name, and Author 3 Name, {``Article Title"}, \emph{Submitted to Conference/Journal Name}, further attributes.
%\\
%$\bullet$ Author 1 Name, Author 2 Name, and Author 3 Name, {``Article Title"}, \emph{Submitted to Conference/Journal Name}, Mon. Year.

% Copyright 2010 Imran Shafique Ansari
% Contact Email: imran.ansari@kaust.edu.sa
% Contact Number: +966 59 897 1005
